Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Tidy the left joined tibble with the positive diagnosis by sample data
Added template code to plot the retro diagnosis by sample

dat.retro %>% 
  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment distribution of the retro cohorts",
       subtitle = paste("N =", dim(dat.retro)[1]),
       x = "",
       y = "") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(mdd_total = n())

@@

dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(anxi_total = n())

@@

>>>>

dat.retro %>% 
  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment distribution of the retro cohorts",
       subtitle = paste("N =", dim(dat.retro)[1]),
       x = "",
       y = "") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(depressive_disorders = n())

@@

dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(anxiety_disorders = n())

@@

```{r Re-organise the positive diagnosis by sample tib}

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('depressive_disorders', 'anxiety_disorders', key = "Diagnosis", value = positive_n)

```{r GLAD/EDGI NBR and RAMP retro diagnosis}

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())
